\thesistitle

### 2019-05-02 sections/background.tex
Wrote some stuff

\section{Clone Class}
Before we go into the refactoring of code clones, we must first define how we identify a clone. Roy \cite{roy2007survey} distinguishes clone pairs, clone classes and clone class families. For this thesis we will consider only ``clone classes'', as the other concepts do not add to the understanding and reasoning of clones as applied in this thesis. Roy defined ``clone classes'' as \textit{the union of all code portions/fragments which are identical or similar to each other}.

As an example, look at the code fragment displayed in figure \ref{fig:cloneclass}. It displays two clone classes. One clone class is in all three files, and has two lines in each file (line 5 and 6). The other clone class is only in the first two files, and has three lines in each file (line 5-7). The clone classes overlap partly.
\begin{figure}[H]
	\includegraphics[width=1\textwidth]{img/clone-class}
	\caption{Simple example of two clone classes, one consisting of three blocks of code of three lines, one existing of two blocks of code of two lines.}
	\label{fig:cloneclass}
\end{figure}

\section{Clone Contexts}
Code clones can be found anywhere in the code. The most commonly studied type of clone is the method-level clone. Method-level clones are duplicated blocks of code in the body of a method. Many clone detection tools only focus on method-level clones (like CPD\footnote{CPD is part of PMD, a commonly used source code analyzer: \url{https://github.com/pmd/pmd}}, Siamese\footnote{Siamese is an Elasticsearch based clone detector: \url{https://github.com/UCL-CREST/Siamese}}, Sysiphus\footnote{Sisyphus crawls the Java library for existing implementations of parts of a codebase: \url{https://github.com/fruffy/Sisyphus}}). The reason for this is that with method-level clones it's most likely that the clones are harmful, and they are more straight-forward to refactor.

A paper by Lozano et al \cite{lozano2007evaluating} discusses the harmfulness of cloning. In this paper the author argues that 98\% are produced at method-level. However, the paper that is cited to support this claim \cite{bergman2004ethnographic} does not conclude this same information. First of all, the study that is referenced uses a very small dataset (460 copy \& paste instances by 11 participants). Secondly, the group of subject only consists og IBM researchers (selection bias). Thirdly, it only focuses on copy and paste instances, as opposed to other ways clones can creep into the code. Finally, the ``98\%'' is not stated explicitly, but is vaguely derivable from one of the figures (figure 1) in this paper. Because of this, there is no reliable overview of how many clones there are in different contexts.

This thesis will focus on measuring how many clones there are per context. This way we can determine the impact of focussing our search on a specific context, like the analysis of only method-level clones. Our hypothesis is that the 98\% claim is not true (we think this should be far less). We also hypothesize that clones in different contexts than method-level are less likely to be harmful and less straight forward to refactor.

@@

\section{Clone Types}
Duplication in code is found in many different forms. Most often duplicated code is the result of a programmer reusing previously written code \cite{haefliger2008code, baxter1998clone}. Sometimes this code is then adapted to fit the new context. To reason about these modifications, several clone types have been proposed. These clone types are described in Roy et al \cite{roy2007survey}:
\begin{displayquote}
\textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
\textbf{Type II:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments.\\
\textbf{Type IV:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.
\end{displayquote}
A higher type of clone means that it's harder to detect and less subtle. There are many studies that adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.

\subsection{Relevance to clone refactoring}
Higher type clones are not only harder to detect, but also harder to refactor. How to refactor clones is heavily dependent on their context and type. Kodhai et al \cite{kodhai2013method} describe different refactorings that can be performed to deal with clones.

For this thesis, we have chosen not to further look at type III and IV clones, as it is very hard to formalize their refactoring processes. They are out of the scope for this thesis.

>>>>

\section{Clone Class}
As code clones are seen as one of the most harmful types of technical debt, they have been studied very extensively. A survey by Roy et al \cite{roy2007survey} states definitions for various important concepts in code clone research. In this survey, he mentions the concept ``clone pair'', which is \textit{a set of two code portions/fragments which are identical or similar to each other}. Furthermore, he defined ``clone class'' as \textit{the union of all clone pairs}. Apart from this, we use the definition ``clone instance'', which is a single code portion/fragment that is part of either a clone pair or clone class.

Figure \ref{fig:clonepair} displays an example of a clone pair or clone class. In this case, both cloned fragments, are found in the same class. Each of the cloned fragments can be defined as a ``clone instance''.

\begin{figure}[H]
	\includegraphics[width=1\textwidth]{img/clone-pair}
	\caption{Example of a clone pair, as found in the \href{https://github.com/taweili/ardublock}{ardublock} project.}
	\label{fig:clonepair}
\end{figure}

Figure \ref{fig:cloneclass} displays two clone classes. These clone classes are separated by a single line that is different. The first clone class spans over both the constructor and a method of this class.

\begin{figure}[H]
	\includegraphics[width=1\textwidth]{img/clone-class}
	\caption{Example of two clone classes.}
	\label{fig:cloneclass}
\end{figure}

\section{Clone Types}
Duplication in code is found in many different forms. Most often duplicated code is the result of a programmer reusing previously written code \cite{haefliger2008code, baxter1998clone}. Sometimes this code is then adapted to fit the new context. To reason about these modifications, several clone types have been proposed. These clone types are described in Roy et al \cite{roy2007survey}:
\begin{displayquote}
\textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
\textbf{Type II:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments.\\
\textbf{Type IV:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.
\end{displayquote}
A higher type of clone means that it's harder to detect and refactor. There are many studies that adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.

Relating this to the clone class example of \ref{fig:cloneclass}, the complete class would be flagged as a type 2 clone. This is displayed in figure \ref{fig:type2cloneclass}. Considering such clones displays the opportunity to refactor the class as a whole.

\begin{figure}[H]
	\includegraphics[width=1\textwidth]{img/type-2-clone-class}
	\caption{The clone displayed in figure \ref{fig:cloneclass} as a type 2 clone.}
	\label{fig:type2cloneclass}
\end{figure}

For this thesis we have chosen not to consider type 4 clones for refactoring, because they are both hard to detect and hard to refactor (how to choose the best alternative for a certain computation could be a thesis in itself).

\section{Clone Contexts} %I don't really like this chapter.
Code clones can be found anywhere in the code. The most commonly studied type of clone is the method-level clone. Method-level clones are duplicated blocks of code in the body of a method. Many clone detection tools only focus on method-level clones (like CPD\footnote{CPD is part of PMD, a commonly used source code analyzer: \url{https://github.com/pmd/pmd}}, Siamese\footnote{Siamese is an Elasticsearch based clone detector: \url{https://github.com/UCL-CREST/Siamese}}, Sysiphus\footnote{Sisyphus crawls the Java library for existing implementations of parts of a codebase: \url{https://github.com/fruffy/Sisyphus}}). The reason for this is that with method-level clones it's most likely that the clones are harmful, and they are more straight-forward to refactor.

A paper by Lozano et al \cite{lozano2007evaluating} discusses the harmfulness of cloning. In this paper the author argues that 98\% are produced at method-level. However, the paper that is cited to support this claim \cite{bergman2004ethnographic} does not conclude this same information. First of all, the study that is referenced uses a very small dataset (460 copy \& paste instances by 11 participants). Secondly, the group of subject only consists of IBM researchers (selection bias). Thirdly, it only focuses on copy and paste instances, as opposed to other ways clones can creep into the code. Finally, the ``98\%'' is not stated explicitly, but is vaguely derivable from one of the figures (figure 1) in this paper. Because of this, there is no reliable overview of how many clones there are in different contexts.

This thesis will focus on measuring how many clones there are per context. This way we can determine the impact of focusing our search on a specific context, like the analysis of only method-level clones. Our hypothesis is that the 98\% claim is not true (we think this should be far less). We also hypothesize that clones in different contexts than method-level are less likely to be harmful and less straight forward to refactor.

@@
